Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-01-19 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\noindent \textbf{Conclusion.} Summarizing, our synthesis tool is capable of presenting a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro. In particular, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the model of the component, nominal current, and voltage. In this respect, even the manufacturer's brand can be presented (in Table~\ref{tab1} it was removed to avoid some advertising).

>>>>

%------------------------------------
\section{Conclusion} 
%------------------------------------

\textcolor{red}{What is the novelty of our work? what are the impacts/relevance of our method to the society and formal methods community? How formal methods can improve the people's life? we should emphasize the relevance of the problem we solve and give numbers to show the efficiency of our approach if compared to HOME Pro.}

Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro. In particular, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the model of the component, nominal current, and voltage. In this respect, even the manufacturer's brand can be presented (\textcolor{red}{shall we add this table online?} in Table~\ref{tab1} it was removed to avoid some advertising).
